---
title: "Data analytics summary"
author: "Jonathan Bourne"
date: "1 February 2016"
output: html_document
---


blah

```{r}
packages <- c("dplyr", "tidyr", "ggplot2")
sapply(packages, library, character.only = TRUE)

setwd("C:/Users/Jonno/Dropbox/Data_Analytics/Data") #change this to your file path

#TwitRetweets <- read.csv(gzfile("twitter_withretweets_daily.csv.gz"), as.is = TRUE)
TwitNoRetweets <- read.csv("twitter_noretweets_daily.csv", as.is = TRUE)

#stocktwits <- read.csv(gzfile("stocktwits_daily.csv.gz"), as.is = TRUE)


```


total number of time units and companies
```{r}
length(unique(TwitNoRetweets$SYMBOL)) %>% paste("Number of unique symbols")
length(unique(TwitNoRetweets$TIMESTAMP_UTC)) %>% paste("Number of unique timestamps", .)
```

summary of each variable

```{r}
summary(TwitNoRetweets)
```


Density plots of all variables except Source, Symbol, Timestamp utc,

The density plots show that almost all the variables are highly skewes except for bull minus bear which is roughly symmetrical. 
```{r}

sapply(c(1:10)[-c(1:3)], function(n) {
  
  plot(density(TwitNoRetweets[,n]), main = names(TwitNoRetweets)[n])
})


```


log Density plots +1 of all variables except Source, Symbol, Timestamp utc, Bull minus Bear

Because of the high level of skew log density plots could give us more information, 1 was added to all values to prevent log zero errors, as there are a lot of zeros

Bull and bear scored messages as well as total scanned messages follow an attenuating peaked pattern
```{r}

sapply(c(1:10)[-c(1:3,6)], function(n) {
  
  plot(density(log10(TwitNoRetweets[,n]+1)), main = names(TwitNoRetweets)[n])
})


```


Aggregate to a reasonable number of groups
plot vs time
Plot densities